Presentation Title

### 2017-07-11 thesis/chapters/ch2-problem.tex
More graphs; consensus protocol analysis

Traditional blockchain systems use PoW as the consensus algorithm.
However, consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since 1982,
where it is first introduced by Lamport et el.~\cite{lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
Since then research in this area picked up pace and many more algorithms are introduced~\cite{abd2005fault, kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

>>>>

Traditional blockchain systems use PoW as the consensus algorithm,
but consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since the 80s~\cite{pease1980reaching, lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
The authors show that running PBFT in Network File System (NFS) was only 3\% slower than the standard unreplicated NFS.
Since then, research in this area picked up pace and many more algorithms are introduced~\cite{abd2005fault, kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

### 2017-07-11 thesis/chapters/ch3-model.tex
More graphs; consensus protocol analysis

In our model we consider $N$ nodes, which is the population size.
$n$ of them are facilitators, $t$ out of $n$ are malicious and the inequalities
$n \ge 3t + 1$ and $N \ge n + t$ must hold.
The first is from the FLP impossibility result TODO.
The second is necessary due to our system design, which becomes clear in TODO.

@@

>>>>

In our model we consider $N$ nodes, which is the population size.
$n$ of them are facilitators, $t$ out of $n$ are malicious and the inequality
$n \ge 3t + 1$ must hold.
This is from the work of Pease, Shostak and Lamport, where they show a network of $n$ nodes cannot reach Byzantine agreement with $t \ge n/3$.
Further, the inequality $N \ge n + t$ must also hold.
This is due to our system design, which becomes clear in~\Cref{sec:consensus-phase}.

@@

\subsection{Privacy preserving validation protocol}
TODO

### 2017-07-11 thesis/chapters/ch4-analysis.tex
More graphs; consensus protocol analysis

\section{Performance}
This section aims to (analytically) answer our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of ACS,
and then the bandwidth requirement for a single transaction.
These are prerequisites of the global throughput analysis.

\subsection{Communication Complexity of ACS}
\label{sec:acs-complexity}
The communication complexity of ACS is $O(n^2|v| + \lambda n^3 \log n)$~\cite{miller2016honey},
where $|v|$ is the size of largest message and $\lambda$ is the security parameter.
Note that the security parameter is the same as the one for our random oracle described in \Cref{sec:model-assumptions}.
In particular, it is from the use of $\textsf{H}(\cdot)$ in the reliable broadcast phase in ACS.
In our system, we wish to understand the scalability properties.
Thus we consider the complexity as a function of $N$ rather than $n$ or $\lambda$.
Since $|v|$ is at most all the CP blocks from every node, we have $|v| = cN$,
where $c$ is a constant representing the size of one CP block.
Therefore the communication complexity of ACS in our system is $O(N)$.
Since we use a constant $n$, $O(N)$ communication complexity also holds for a single facilitator.

@@

\subsection{Time Complexity of ACS}
\label{sec:acs-time-complexity}
In order to make arguments on bandwidth or throughput, which are concepts that depend on time,
we must make some assumptions on the time complexity of ACS.
The time complexity we use here is not the same as what is typically used in distributed systems.
In analysis of distributed systems, time complexity is often in number of rounds.
For example, ACS runs in a constant number of rounds because its subprotocols---reliable broadcast and binary Byzantine consensus---also run in a constant number of rounds.
However, in practice, making a unit of communication always has some overhead associated with it, for example serialising and writing it to some network socket.
Hence, for the remainder of our performance analysis, add the following to our computational model.
For every unit of communication, we assume they take some non-negligible but constant time to perform.
From our result in \Cref{sec:acs-complexity} and the fact that ACS runs in a constant number of rounds,
it follows that ACS has a time complexity of $O(N)$.

\subsection{Communication Cost for Transactions}
\label{sec:communication-cost-for-tx}
With our assumption on the time complexity of ACS,
we are ready to analyse the amount of data required to be transmitted over a link per transaction,
which we call the communication cost per transaction.
% First, we define bandwidth as the ``amount of data a link or network path can deliver per unit of
% time''~\cite{prasad2003bandwidth}.
We know that to create and then validate a transaction,
the communication cost per transaction is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment,
the other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{acs}},$$
where $D_{\text{acs}}$ is the duration an instance of ACS.
But from \Cref{sec:acs-time-complexity},
we know that $D_{\text{acs}}$ is of $O(N)$, thus the communication per transaction is $O(N)$.
This is intuitive because consensus duration would be longer if there are more CP blocks, which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
The behaviour is also verified experimentally in \Cref{ch:implementation}.

>>>>

\section{Performance}
This section aims to analytically answer our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of the consensus protocol,
and then the bandwidth requirement for a single transaction.
We build on top of those results to analyse do the global throughput analysis.

\subsection{Communication complexity of the consensus protocol}
\label{sec:acs-complexity}
The consensus protocol can bee seen as three parts.
Thus the communication complexity is the sum of these three parts.
The first part is when every node sends their CP block to all the facilitators, which is $O(Nn)$ since there are $N$ nodes and $n$ facilitators.
Or simply $O(N)$ if we consider $n$ as a constant.

The second part is ACS.
The communication complexity of ACS is $O(n^2|v| + \lambda n^3 \log n)$~\cite{miller2016honey},
where $|v|$ is the size of largest message and $\lambda$ is the security parameter.
Note that the security parameter is the same as the one for our random oracle described in \Cref{sec:model-assumptions}.
In particular, it is from the use of $\textsf{H}(\cdot)$ in the reliable broadcast phase in ACS.
In our system, we wish to understand the scalability properties.
Thus we consider the complexity as a function of $N$ rather than $n$ or $\lambda$.
Since $|v|$ is at most all the CP blocks from every node, we have $|v| = cN$,
where $c$ is a constant representing the size of one CP block.
Therefore the communication complexity of ACS in our system is $O(N)$.
Since we use a constant $n$, $O(N)$ communication complexity also holds for a single facilitator.

The third and final part is the dissemination, where the facilitators broadcast the consensus result along with their signatures.
For the same reason as the first part, this is also $O(N)$.
Thus the combined communication complexity when $n$ is a constant is $O(N)$.

@@

\subsection{Time complexity of the consensus protocol}
\label{sec:acs-time-complexity}
In order to make arguments on bandwidth or throughput, which are concepts that depend on time,
we must make some assumptions on the time complexity of consensus protocol.
The time complexity we use here is not the same as what is typically used in distributed systems.
In analysis of distributed systems, time complexity is often in terms of the number of rounds.
For example, ACS runs in a constant number of rounds because its subprotocols---reliable broadcast and binary Byzantine consensus---also run in a constant number of rounds.
However, in practice, making a unit of communication always has some overhead associated with it, for example serialising and writing it to some network socket.
Hence, for the remainder of our performance analysis, we add the following to our computational model.
For every unit of communication, we assume they take some non-negligible but constant time to perform.
Hence, from~\Cref{sec:acs-complexity}, it directly follows that the consensus protocol has a time complexity of $O(N)$.

\subsection{Communication Cost for Transactions}
\label{sec:communication-cost-for-tx}
With the analysis on the time complexity of consensus protocol,
we are ready to analyse the amount of data required to be transmitted over a link per transaction,
which we call the communication cost per transaction.
% First, we define bandwidth as the ``amount of data a link or network path can deliver per unit of
% time''~\cite{prasad2003bandwidth}.
We know that to create and then validate a transaction,
the communication cost per transaction is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment.
The other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{c}},$$
where $D_{\text{c}}$ is the duration a round of the consensus protocol.
But from \Cref{sec:acs-time-complexity},
we know that $D_{\text{c}}$ is of $O(N)$, thus the communication cost per transaction is $O(N)$.
This is intuitive because round duration would be longer if there are more CP blocks (more $N$), which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
The behaviour is also verified experimentally in \Cref{ch:implementation}.

### 2017-07-11 thesis/chapters/ch5-implementation.tex
Write some optimisation
More graphs; consensus protocol analysis

@@

\section{Communication Cost for Consensus}

\begin{figure}[h]
  \centering
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/consensus-communication-cost-vs-population}
    \caption{Transactions are with fixed neighbours}
    \label{fig:consensus-comms-fixed}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/consensus-communication-cost-vs-population}
    \caption{Transactions are with random neighbours}
    \label{fig:consensus-comms-random}
  \end{subfigure}
  \caption{Communication cost for consensus}
  \label{fig:consensus-comms}
\end{figure}

>>>>

Finally, the cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.
Both of which are provided by libnacl~\footnote{\url{https://pypi.python.org/pypi/libnacl}}.

@@

\section{Communication cost for a round}

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=1.0\textwidth]{neighbour-fixed/round-communication-cost-vs-population}
      \caption{Transactions are with fixed neighbours}
      \label{fig:consensus-comms-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=1.0\textwidth]{neighbour-random/round-communication-cost-vs-population}
      \caption{Transactions are with random neighbours}
      \label{fig:consensus-comms-random}
    \end{subfigure}%
  }
\end{figure}
